Copy number inference with InferCNV

### 2024-05-20 analyses/cell-type-ewings/exploratory_analysis/04-infercnv.Rmd
move notebook to exploratory analysis

all_results_dir_list <- c(
  no_ref = file.path(results_dir, "no_reference"),
  with_ref = file.path(results_dir, "endothelial_reference")
)

@@

cnv_df <- cnv_df |>
  # get total number of cnvs per cell and then scale that number 
  dplyr::mutate(has_cnv = rowSums(across(has_cnv_cols)),
                scaled_cnv = scale(has_cnv))
```

@@

ggplot(cnv_df, aes(x= scaled_cnv)) + 
  geom_density() +
  theme_bw() +
  labs(x = "Scaled number of CNVS")
```

>>>>

all_results_dir_list <- list(
  no_ref = file.path(results_dir, "no_reference"),
  with_ref = file.path(results_dir, "endothelial_reference")
)

@@

cnv_df <- cnv_df |>
  # get total number of chromosomes with cnvs per cell and then scale that number 
  dplyr::mutate(has_cnv = rowSums(across(has_cnv_cols)),
                scaled_cnv = scale(has_cnv))
```

@@

ggplot(cnv_df, aes(x= scaled_cnv)) + 
  geom_density() +
  theme_bw() +
  labs(x = "z-scaled chromosome CNV count")
```
